Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
Uncertainty analysis

For each province, we take a 7 day rolling sum on the number of new cases each day, and feed the data into the parametric SI model, which is given distribution $w(\tau)$ From there, the model uses a likelihood based approach to estiamte R at each discrete timestep, computing the likelihood that a person at timestep $i$ is infected by a person infected at timestep $j$, and summing the likelihood for each $j$ across all its infectees to compute the $R$ value at timestep $j$. Thus, for each province, we produce a daily time series estimate for $R$ on each day. This method is outlined in detail in Wallinga and Teunis (2004)[8].

For each province, day pair, we have $\bar{x} = (x_1, x_2, x_3, x_4), y$ where:

- $x_1$: standardized GDP per capita
- $x_2$: standardized population density
- $x_3$: standardized air temperature
- $x_4$: standardized relative humidity
- $y$: logarithm of estimated R

We then perform ordinary least squares regression to find $\bar{\beta}$:
$$
y = \beta_0 + \beta_1x_1 + \beta_2x_2 + \beta_3 x_3 + \beta_4 x_4 + \varepsilon
$$

@@

@@

## Discussion
Our model suggests that there is some weak evidence that with increasing temperature, the reproductive number R decreases. The effect of relative humidity on the reproductive number is much less conclusive. As we only used data from Italy in our model building, there is a limited range of weather information than we would like to have.

>>>>

For each province, we take a 7 day rolling sum on the number of new cases each day, and feed the data into the parametric SI model, which is given distribution $w(\tau)$ From there, the model uses a likelihood based approach to estiamte R at each discrete timestep, computing the likelihood that a person at timestep $i$ is infected by a person infected at timestep $j$, and summing the likelihood for each $j$ across all its infectees to compute the $R$ value at timestep $j$. This method is outlined in detail in Wallinga and Teunis (2004)[8].

@@

[What methods/models are best]
[What condition(s) does each method/model work well/poorly]
[Conclusion about dataset]

@@

## Discussion
